### 2022-02-18 sections/conclusion.tex
minor update

%-------------------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
%-------------------------------------------------------------------------------
A search for flavour-changing neutral current processes involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented. FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$. The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$. The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a b-tagged jet as well as multiple jets. Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.
%The search sensitivities have been improved significantly compared to the previous analysis using 36$^{-1}$ of run-2 data~\cite{Aaboud2019SearchFT}. 
%No significant excess of events above the background expectation is found.
A slight excess of data is observed above background with a significance of 2.6$\sigma$.  
We set 95\% CL upper limits on the $t\to Hq$ branching ratios and the corresponding
dimension-6 operator Wilson coefficients in the effective $tqH$ couplings. 
%about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Table~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9\times10^{-4}$ ($5.0^{+2.2}_{-1.4}\times10^{-4}$) and $7.2\times10^{-4}$ ($3.6^{+1.7}_{-1.0}\times10^{-4}$).
%The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are set to $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$, respectively.
The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.
These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios..

>>>>

%-------------------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
%-------------------------------------------------------------------------------
A search for flavour-changing neutral current processes involving a top quark, an up-type quark ($q=u, c$), and a SM Higgs boson is presented. FCNC $tqH$ interaction is searched for both in $t\bar{t}$ decay mode, where one top quark decays following SM processes and the other one decays through $t\rightarrow Hq$, and in production mode ($pp\rightarrow tH$) with a single top quark produced via FCNC interaction where $t\to Wb$. The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the CERN Large Hadron Collider and corresponding to an integrated luminosity of 139 fb$^{-1}$. The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$), a b-tagged jet as well as multiple jets. Multivariate techniques based on BDT are used to distinguish the signal from the background on the basis of their different kinematics.
%The search sensitivities have been improved significantly compared to the previous analysis using 36$^{-1}$ of run-2 data~\cite{Aaboud2019SearchFT}. 
%No significant excess of events above the background expectation is found.
A slight excess of data is observed above background with a significance of 2.6$\sigma$.  
We set 95\% CL upper limits on the $t\to Hq$ branching ratios and the corresponding
dimension-6 operator Wilson coefficients in the effective $tqH$ couplings. 
%about a factor of 2 improvement to 95\% CL upper limits on the $t\to Hq$ branching ratios are reported in Table~\ref{tab:limits_summary}, along with the Wilson coefficients with respect to the previous partial run-2 results~\cite{Aaboud2019SearchFT}.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9\times10^{-4}$ ($5.0^{+2.2}_{-1.4}\times10^{-4}$) and $7.2\times10^{-4}$ ($3.6^{+1.7}_{-1.0}\times10^{-4}$).
%The observed (expected) upper limits on the D6 Wilson coefficients from the combination of the searches are set to $C_{c\phi}<1.38\,(0.97)$ and $C_{u\phi}<1.18\,(0.83)$, respectively.
The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$, respectively.
These results improve significantly upon previous ATLAS and CMS limits on the $t\rightarrow Hq$ branching ratios.

### 2022-02-18 sections/introduction.tex
minor update

In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small $\BR(t\to qH)$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM.
%The assumption of using SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}. 
%Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
%Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
%has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
%and excellent diphoton mass re\-so\-lu\-tion. 
%Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
%are able to exploit a branching ratio that is significantly larger for the $H \rightarrow WW^*, \tau\tau$ decay modes than for the $H \rightarrow \gamma\gamma$ decay mode,
%are able to exploit a significantly larger branching ratio for the Higgs boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, 
%and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
%Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
%of $\BR(H\to b\bar{b})\simeq 58\%$.
Compared to Run~1, the Run~2 searches (Table~\ref{tab:limits_summary_ref}) benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton (electron or muon) signatures resulting from 
$H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau^+\tau^-$ decay in which at least
one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
%The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
Combining all of the ATLAS searches using 36.1~fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.

The CMS Collaboration performed a similar search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to cH)<0.47\%$ and $\BR(t\to uH)<0.47\%$, in each case neglecting the other decay mode.
Compared with previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}.

@@

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
The analysis targets Higgs boson decays to 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018. The corresponding integrated luminosity is 139.0 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. The signals are divided into several final states depending on the production mode and
the  $W$ boson decay either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected as the hadronic channels. Events with at least one \tauhad with an additional electron or muon are selected as the leptonic channels. More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data and more
$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique, boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.

>>>>

In these searches, one of the top quarks is required to decay into $Wb$, while the other top quark decays into $qH$ with a small $\BR(t\to qH)$, yielding $\ttbar \to WbHq$.\footnote{In the following, $WbHq$ is used to denote both $W^+b H\bar{q}$ and its charge conjugate, $HqW^- \bar{b}$. Similarly, 
$WbWb$ is used to denote $W^+b W^- \bar{b}$.}  The Higgs boson is assumed to have a mass of $m_H=125~\gev$ and to decay as predicted by
the SM.
%The assumption of using SM-like Higgs boson branching ratios is motivated by the fact that measurements of the flavour-diagonal Higgs boson couplings by the ATLAS and CMS collaborations are in agreement with the SM prediction within about 10\%~\cite{Khachatryan:2016vau,Sirunyan:2018koj}. 
%Furthermore, typical beyond-the-SM scenarios that predict significant enhancements to $\BR(t\to Hq)$, also predict modifications to the Higgs boson branching ratios at the few percent level or below, well beyond the current experimental precision.
%Some of the most sensitive single-channel searches have been performed in the $H\to\gamma\gamma$ decay mode, which
%has a small branching ratio of $\BR(H\to \gamma\gamma)\simeq 0.2\%$, but benefits from having a very small background contamination 
%and excellent diphoton mass re\-so\-lu\-tion. 
%Searches targeting signatures with two same-charge leptons or three leptons (electrons or muons), generically referred to as multileptons,
%are able to exploit a branching ratio that is significantly larger for the $H \rightarrow WW^*, \tau\tau$ decay modes than for the $H \rightarrow \gamma\gamma$ decay mode,
%are able to exploit a significantly larger branching ratio for the Higgs boson decay into $H \to WW^*, \tau\tau$ compared to the $H\to\gamma\gamma$ decay mode, 
%and are also characterised by relatively small backgrounds.
%However, in general they do not have good mass resolution,\footnote{An exception is the $H\to ZZ^*\to \ell^+\ell^- \ell^{\prime +}\ell^{\prime -}$ 
%($\ell, \ell^\prime = e, \mu$) decay mode, which has a very small branching ratio and thus is not promising for this search.} 
%so any excess would be hard to interpret as originating from $t \to Hq$ decays.
%Finally, searches have also been performed exploiting the dominant Higgs boson decay mode, $H\to b\bar{b}$, which has a branching ratio 
%of $\BR(H\to b\bar{b})\simeq 58\%$.
Compared to Run~1, the Run~2 searches, summarised in Table~\ref{tab:limits_summary_ref}, benefit from the increased $\ttbar$ cross section at $\sqrt{s}=13~\tev$, as well as the larger integrated luminosity.
Using 36.1~fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, the ATLAS Collaboration has derived upper limits at 95\% confidence level (CL) of
$\BR(t\to cH)<0.22\%$ using $H\to \gamma\gamma$ decays~\cite{Aaboud:2017mfd}, $\BR(t\to cH)<0.16\%$ based on
%signatures with two same-charge light leptons (electrons or muons) or three light leptons 
multilepton (electron or muon) signatures resulting from 
$H \to  WW^*, ZZ^*$, $H\to \tau^+\tau^-$ in which both $\tau$-leptons decay leptonically~\cite{Aaboud:2018pob},
$\BR(t\to cH)<0.42\%$ using $H\to b\bar{b}$ decay~\cite{fcnc36}, and of $\BR(t\to cH)<0.19\%$ using $H\to \tau^+\tau^-$ decay in which at least
one of $\tau$-leptons decays hadronically~\cite{fcnc36}.  
These upper limits are derived assuming that $\BR(t\to uH)=0$. Similar upper limits are obtained for $\BR(t\to uH)$ assuming $\BR(t\to cH)=0$.
%The searches with  $H\to \tau^+\tau^-$ and $H\to b\bar{b}$ decays are later published~\cite{fcnc36}, unfortunately with no FCNC signal found.
Combining all of the ATLAS searches using 36.1~fb$^{-1}$ Run~2 data, the limits at 95\% CL are set for  $\BR(t\to cH)<0.11\%$ and $\BR(t\to uH)<0.12\%$ respectively assuming $\BR(t\to uH)=0$ and $\BR(t\to cH)=0$~\cite{fcnc36}.

The CMS Collaboration performed a similar search using  
$H\to b\bar{b}$ decays~\cite{Sirunyan:2017uae} with 35.9 fb$^{-1}$ of data at $\sqrt{s}=13~\tev$, resulting 
in upper limits of $\BR(t\to cH)<0.47\%$ and $\BR(t\to uH)<0.47\%$, in each case neglecting the other decay mode.
Compared with previous searches, the search in Ref.~\cite{Sirunyan:2017uae} considers in addition the contribution to the signal from 
$pp \to tH$ production~\cite{Greljo:2014dka}. CMS recently updated their search for $tqH$ in the $H\to b\bar{b}$ channel using
their full Run-2 data and  set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $7.9\times10^{-4}(1.1\times10^{-3})$ and $\mathcal{B}(t\to Hc)$ of $9.4\times10^{-4}(8.6\times10^{-4})$~\cite{CMS:2021gfa}.
CMS also recently reported a search for $tqH$ in the $H\rightarrow \gamma\gamma$ mode using the full Run-2 data and set observed(expected) upper limits on $\mathcal{B}(t\to Hu)$ of $1.9\times10^{-4}(3.1\times10^{-4})$ and $\mathcal{B}(t\to Hc)$ of $7.3\times10^{-4}(5.1\times10^{-4})$~\cite{CMS-PAS-TOP-20-007}.

@@

%This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018.
This analysis targets Higgs boson decays to 
%This paper is focused on the decay mode of the Higgs boson into
$\tau$-leptons with the complete Run~2 dataset collected in 2015-2018. The corresponding integrated luminosity is 139.0 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. The signals are divided into several final states depending on the production mode and
the  $W$ boson decay either hadronically or leptonically from the $t\rightarrow Wb$ decay, which are referred as $t_h$ and $t_l$. The contribution of $W\rightarrow\tau\nu$ is included either in
$t_l$ when the $\tau$ decays into a light lepton (electron or muon) as $\tau_{\text{lep}}$ or in $t_h$ when the $\tau$ decays hadronically as $\thad$.
The $H\rightarrow \tau\tau$ decay is detected in
either $\tlhad$ or $\thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected as the hadronic channels. Events with at least one \tauhad with an additional electron or muon are selected as the leptonic channels. More signal regions are exploited here compared to the previous FCNC $\Htautau$ search conducted using partial Run~2 data and more
$t\bar{t}$ control regions (CRtt) are used for calibration of misidentified (fake) taus in Monte Carlo and data-driven fake estimations from QCD multi-jet background.
Finally, a multivariate technique, boosted decision trees, is used to discriminate between the signal and the background on the basis of their different kinematics distributions.

### 2022-02-18 sections/statistical_analysis.tex
minor update

The final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(qH)$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to Gaussian constraints in the likelihood.
For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
according to the corresponding systematic uncertainties, and their fitted values result in the deviations from
the nominal expectations that globally provide the best fit to the data.
This procedure allows a reduction of the impact of systematic uncertainties on 
the search sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
%To verify the improved background prediction, fits under the background-only hypothesis are performed, 
%and differences between the data and the post-fit background prediction are checked 
%using kinematic variables other than the ones used in the fit. 
Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account by dedicated parameters in the fit.     
The best-fit $\BR(t\to qH)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
hypothesis, maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.

The fitting procedure was initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
a signal contamination above 10\% are excluded (referred to as blinding requirements).
In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions about some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
fit is able to correctly determine the strength of a simulated signal injected into the real data.

>>>>

The final BDT discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(qH)$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to Gaussian constraints in the likelihood.
For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
according to the corresponding systematic uncertainties, and their fitted values result in the deviations from
the nominal expectations that globally provide the best fit to the data.
This procedure allows a reduction of the impact of systematic uncertainties on 
the search sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
%To verify the improved background prediction, fits under the background-only hypothesis are performed, 
%and differences between the data and the post-fit background prediction are checked 
%using kinematic variables other than the ones used in the fit. 
Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account by dedicated parameters in the fit.     
The best-fit $\BR(t\to qH)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
hypothesis, maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.

The fitting procedure was initially validated through extensive studies using pseudo data, defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
a signal contamination above 10\% are excluded (referred to as blinding requirements).
In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions about some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
fit is able to correctly determine the strength of a simulated signal injected into the real data.

### 2022-02-18 sections/strategy_Htautau.tex
minor update

%%%%%%%%%%%%%%%
\begin{table*}[t!]
  \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
      The values in percent (\%) represent the separation and importance of each variable.
    The descriptions of each variable are provided in the following text.}}
\label{tab:importance_xTFW}
\input{tables/xTFW_Merged}
\end{table*}

\begin{table*}[t!]
  \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
      The values in percent (\%) represent the separation and importance of each variable.
    The descriptions of each variable are provided in the following text.}}
\label{tab:importance_tthML}
\input{tables/tthML_Merged}
\end{table*}

>>>>

%%%%%%%%%%%%%%%
\begin{table*}[t!]
  \caption{\small{The number of discriminating variables (n) used in the training of BDT in each SR. Variables are ranked from highest (1) to lowest (n) relative to one another by their
      importance in the training. Variables which do not have a ranking are not included in the training. 
      %The values represent their ra importance rankings of each variable and cross($\times$) denotes the variable is not used in the training.
      The descriptions of each variable are provided in the following text.}}
\label{tab:importance}
 \begin{tabular}{cccccccc} \toprule\toprule
   & $t_{l}\tauhad$-1j                                  &  $t_{h}\tlhad$-2j   &  $t_{l}\tauhad$-2j & $t_{h}\tlhad$-3j & $t_l\thadhad$     & $t_h\thadhad$-2j & $t_h\thadhad$-3j       \\\midrule
   Total variables~(n)                           & $12$ & $15$ & $12$ & $17$ & $15$ & $12$ & $12$ \\\midrule 
 $m_{\text{W}}$                                      &   &             &           & $9$      &       & $6$      & $7$\\
 $\chi^{2}$                                          &   &             &           & $14$     &       &  &       \\
 \text{max}($\eta_{\tau}$)                           & $4$       &             &  $4$              &  & $10$          &  &        \\
 $m^{\text{T}}_{\text{W}}$                           & $11$      &             &  $8$              &  & $13$          &  &         \\
 $m_{\tau,\tau}$                                     &   &  $2$                &           & $3$      &       & $1$      & $1$          \\
 $m_{\text{t},\text{SM}}$                            &   &  $1$                &           & $2$      &       & $3$      & $4$          \\
 $p_{\text{T},\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\
 $m_{\text{t},\text{FCNC}}$                          &   &             &           &  &       & $10$     & $6$\\
 $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &             &  $5$              &  & $4$           &  &         \\
 $p_{\text{T},\tau}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
 $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
 $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
 $E_{\text{vis}~\tau,1}/E_{\tau,1}$                  &   &  $10$               &           & $12$     &       & $8$    & $8$          \\
 $E_{\text{vis}~\tau,2}/E_{\tau,2}$                  &   &  $7$                &           & $4$      &       & $9$    & $11$         \\
 $P_{\text{T,\tauhadvis}} $                          &   &             &           &  & $9$           &  &         \\
 $m_{\text{t},\text{FCNC},\text{vis}}$               &   &             &           &  & $3$           &  &        \\
 $\Delta\phi(\tau\tau,\met)$                         &   &  $6$                            &           & $16$     &       & $13$   & $12$         \\
 $\met\text{centrality}$                             &   &  $13$               &           & $15$     &       & $12$   & $9$         \\
 \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &             &  $3$              &  & $14$          &  &         \\
 $\Delta R(\ell,\tau)$                               & $8$       &  $9$                &  $9$              & $10$     & $15$          &  &         \\
 $\Delta R(\tau,\tau)$                               &   &             &           &  & $2$           & $4$    & $3$             \\
 $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          &  &         \\
 $\Delta R(\tau,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          &  &        \\
 $\Delta R(\ell+\text{b-jet},\tau\tau )$             &   &             &           &  & $7$           &  &         \\
 $\Delta R(\tau,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
 \text{Min}($m_{\text{light-jet},\text{light-jet}}$) &   &  $12$               &           & $11$     &       &  &         \\
% $m_{\text{W}}$                                      & $\times$  &  $\times$           &  $\times$         & $9$      & $\times$      & $6$      & $7$\\
% $\chi^{2}$                                          & $\times$  &  $\times$           &  $\times$         & $14$     & $\times$      & $\times$ & $\times$      \\
% \text{max}($\eta_{\tau}$)                           & $4$       &  $\times$           &  $4$              & $\times$ & $10$          & $\times$ & $\times$       \\
% $m^{\text{T}}_{\text{W}}$                           & $10$      &  $\times$           &  $8$              & $\times$ & $13$          & $\times$ & $\times$        \\
% $m_{\tau,\tau}$                                     & $\times$  &  $2$                &  $\times$         & $3$      & $\times$      & $1$      & $1$          \\
% $m_{\text{t},\text{SM}}$                            & $\times$  &  $1$                &  $\times$         & $2$      & $\times$      & $3$      & $4$          \\
% $p_{\text{T},\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     & $\times$      & $\times$ & $\times$        \\
% $m_{\text{t},\text{FCNC}}$                          &  $\times$ &  $\times$           &  $\times$         & $\times$ & $\times$      & $10$     & $6$\\
% $m_{\text{t},\text{SM},\text{vis}}$                 & $3$       &  $\times$           &  $5$              & $\times$ & $4$           & $\times$ & $\times$        \\
% $p_{\text{T},\tau}$                                 & $1$       &  $4$                &  $1$              & $1$      & $5$           & $11$   & $10$           \\
% $\met$                                              & $5$       &  $11$               &  $10$             & $13$     & $6$           & $7$    & $13$          \\
% $m_{\tau\tau,\text{vis}}$                           & $10$      &  $14$               &  $11$             & $6$      & $1$           & $2$    & $2$          \\
% $E_{\text{vis}~\tau,1}/E_{\tau,1}$                  & $\times$  &  $10$               &  $\times$         & $12$     & $\times$      & $8$    & $8$          \\
% $E_{\text{vis}~\tau,2}/E_{\tau,2}$                  & $\times$  &  $7$                &  $\times$         & $4$      & $\times$      & $9$    & $11$         \\
% $P_{\text{T,\tauhadvis}} $                          & $\times$  &  $\times$           &  $\times$         & $\times$ & $9$           & $\times$ & $\times$        \\
% $m_{\text{t},\text{FCNC},\text{vis}}$               & $\times$  &  $\times$           &  $\times$         & $\times$ & $3$           & $\times$ & $\times$       \\
% $\Delta\phi(\tau\tau,\met)$                         & $\times$  &  $6$    			   &  $\times$         & $16$     & $\times$      & $13$   & $12$         \\
% $\met\text{centrality}$                             & $\times$  &  $13$               &  $\times$         & $15$     & $\times$      & $12$   & $9$         \\
% \text{Min}($m_{\tau\tau \text{q-jet}}$)             & $9$       &  $\times$           &  $3$              & $\times$ & $14$          & $\times$ & $\times$        \\
% $\Delta R(\ell,\tau)$                               & $8$       &  $9$                &  $9$              & $10$     & $15$          & $\times$ & $\times$        \\
% $\Delta R(\tau,\tau)$                               & $\times$  &  $\times$           &  $\times$         & $\times$ & $2$           & $4$    & $3$             \\
% $\Delta R(\ell,\text{b-jet})$                       & $2$       &  $3$                &  $2$              & $8$      & $12$          & $\times$ & $\times$        \\
% $\Delta R(\tau,\text{b-jet})$                       & $6$       &  $5$                &  $6$              & $7$      & $11$          & $\times$ & $\times$       \\
% $\Delta R(\ell+\text{b-jet},\tau\tau )$             & $\times$  &  $\times$           &  $\times$         & $\times$ & $7$           & $\times$ & $\times$        \\
% $\Delta R(\tau,\text{light-jet})$                   & $7$       &  $8$                &  $7$              & $5$      & $8$           & $5$    & $5$    \\
% \text{Min}($m_{\text{light-jet},\text{light-jet}}$) & $\times$  &  $12$               &  $\times$         & $11$     & $\times$      & $\times$ & $\times$        \\
 \bottomrule\bottomrule\\
\end{table*}

%%%%%%%%%%%%%%%
%%%  \begin{table*}[t!]
%%%    \caption{\small{Discriminating variables used in the training of the BDT for hadronic channel.
%%%        The values in percent (\%) represent the separation and importance of each variable.
%%%      The descriptions of each variable are provided in the following text.}}
%%%  \label{tab:importance_xTFW}
%%%  \input{tables/xTFW_Merged}
%%%  \end{table*}
%%%  
%%%  \begin{table*}[t!]
%%%    \caption{\small{Discriminating variables used in the training of the BDT for leptonic channel.
%%%        The values in percent (\%) represent the separation and importance of each variable.
%%%      The descriptions of each variable are provided in the following text.}}
%%%  \label{tab:importance_tthML}
%%%  \input{tables/tthML_Merged}
%%%  \end{table*}

### 2022-02-18 sections/systematic_uncertainties.tex
minor update

Uncertainties associated with jets arise from the jet energy scale
and resolution, and the efficiency to pass the JVT requirements. 
The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment, 
is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertainty is
below 5\% for most jets and below 1\% for central jets with pT between 300 GeV and 2 TeV. The difference between the JER
in data and MC is represented by one NP. It is applied on the MC by smearing the jet pT within the prescribed uncertainty.

@@

The hdamp parameter (which controls the amount of radiation produced by the parton shower in
POWHEG-BOX v2) is set to 1.5$m_{top}$ in the nominal case. Alternative samples are generated with hdamp=3$m_{top}$. The
difference between two samples is treated as one of the systematics as ``$t\bar{t}$ hdamp''. 
%The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
%{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix-element calculation is performed 
%for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
%merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.

>>>>

Uncertainties associated with jets arise from the jet energy scale
and resolution, and the efficiency to pass the JVT requirements. 
The largest contribution results from the jet energy scale, whose uncertainty dependence on jet $\pt$ and $\eta$, jet flavour, and pile-up treatment, 
is split into 43 uncorrelated components that are treated independently~\cite{Aaboud:2017jcu}. The total JES uncertainty is
below 5\% for most jets and below 1\% for central jets with $\pt$ between 300 GeV and 2 TeV. The difference between the JER
in data and MC is represented by one NP. It is applied on the MC by smearing the jet $\pt$ within the prescribed uncertainty.

@@

The hdamp parameter (which controls the amount of radiation produced by the parton shower in
POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with hdamp=3$m_t$. The
difference between two samples is treated as one of the systematics as ``$t\bar{t}$ hdamp''. 
%The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
%{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix-element calculation is performed 
%for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
%merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.
